How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-15 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

___
**Box 1: Examples of boilerplate text (Statistical software)**

@@

___
**Box 2: Examples of boilerplate text (Between-group hypothesis testing, two groups)**

@@

The clustering algorithm found groups that were purely sample size calculations (topic 2), pilot studies (topic 5) and repeated measures ANOVA (topic 10). There were cases where the exact same method section had been ...

@@

The first line in many statistical analysis sections in _PLOS ONE_ was the software used and some entire sections in ANZCTR only stated the software, implying that the software is the most important detail. As Doug Altman said, "Many people think that all you need to do statistics is a computer and appropriate software" [@Altman1994]. This is not the case, and whilst it is important for researchers to mention the software and version used for reproducibility purposes, it is a minor detail compared with detailing what methods were used and why.

>>>>

___
**Box 1: Examples of boilerplate text from _PLOS ONE_ (Statistical software)**

@@

___
**Box 2: Examples of boilerplate text from _PLOS ONE_ (Between-group hypothesis testing, two groups)**

@@

The clustering algorithm found groups that were purely sample size calculations (topic 2), pilot studies (topic 5), safety/tolerability studies (topic 6) and repeated measures ANOVA (topic 10). There were cases where the exact same method section had been ...

We also found evidence of 'boilerplate' sections clustered as topic 3, example text

___
**Box x: Examples of boilerplate text from ANZCTR**

* "Shapiro Wilk test was used as normality test. Continuous variables were compared using Student t-test and Mann-Whitney U test when the data were not normally distributed. Categorical variables were compared using Pearson’s chi-squared test and Fisher’s exact test. Paired data were analyzed using Paired t-test and Wilcoxon signed rank test when data were not normally distributed"
* "Comparisons between categorical variables will be made either using chi square or Fisher exact test. Continuous data will be compared using the Student’s t-test or Mann-Whitney U test. Two sided p values of less than 0.05 will be considered statistically significant."
___

@@

The first line in many statistical analysis sections in _PLOS ONE_ was the software used and some entire sections in ANZCTR only stated the software, implying that the software is the most important detail. As Doug Altman said, "Many people think that all you need to do statistics is a computer and appropriate software" [@Altman1994]. This is far from the truth, and whilst it is important for researchers to mention the software and version used for reproducibility purposes, it is a minor detail compared with detailing what methods were used and why.

A frequent theme in the boilerplate statistical methods is the definition of statistical significance, nearly always using a p-value at the 5% level. This widespread use of statistical significance is troubling giving the bright-line thinking it engenders [mcshane] and the common misinterpretations of p-values [goodman].
